A Gentle Introduction to Structural Causal Models

### 2021-05-21 presentation_video.Rmd

- Machine learning has provided many insights into different problems 
- One issue is the consideration of 'What are we actually predicting'?
- Mainstream tools are build on association-based learning 
- Associations are not enough for high stake settings 
- In disciplines like psychology or economics people are less interested in associational learning
- We want causation and not correlation

@@

* Foundations of SCMs 
* Assumptions 
  * Comparative Causal Tools 
  * Historical Development 
* Pearl's Causal Hierachy 
  * Prediction 
  * Intervention 
  * Counterfactuals 
  * Implications 
* Graphical Models 
  * Features 
  * Implications
* Causality and Time

@@

- The second query deals with interventions
- Here we can use do-calculus
- The do-calculus enables us to study the manipulation of parent nodes
- There are various types of intervention
- One example is **atomic intervention,** where we set a variable to a constant
- In **policy intervention** we specify a different function for an equation
- Off-policy intervention models different intervention that is not in our historical data
- CBN , MDP and reinforcement learning model intervention.

>>>>

- Machine learning has provided many insights into different problems 
- One issue is the consideration of 'What are we actually predicting'?
- Mainstream tools are build on association-based learning 
- Associations are not enough for high stake settings 
- We want causation and not correlation

@@

* Foundations of SCMs 
  * Assumptions 
  * Comparing Causal Tools 
* Pearl's Causal Hierachy 
  * Prediction 
  * Intervention 
  * Counterfactuals 
  * Implications 
* Graphical Models 
  * Features 
  * Implications
* Causality and Time

@@

- The second query deals with interventions
- Mathematical Tool: do-calculus
- The do-calculus enables us to study the manipulation of parent nodes
- There are various types of intervention
- One example is **atomic intervention,** where we set a variable to a constant
- In **policy intervention** we specify a different function for an equation
- Off-policy intervention models different intervention that is not in our historical data
- CBN , MDP and reinforcement learning model intervention.
